\documentclass[a4paper, serif, 12pt]{moderncv}

%% moderncv
% style and color
\moderncvstyle{banking}
\moderncvcolor{black}

%% page layout/margins
\usepackage[top=1.5cm, bottom=1.5cm, left=2.0cm, right=2.0cm]{geometry}

%% Babel config for English language
\usepackage[english]{babel}

%% fontspec
\usepackage{fontspec}

\IfFontExistsTF{Linux Libertine}{
  \setmainfont[Ligatures={TeX, Common}, Numbers=OldStyle]{Linux Libertine}
}{}
\IfFontExistsTF{Linux Libertine O}{
  \setmainfont[Ligatures={TeX, Common}, Numbers=OldStyle]{Linux Libertine O}
}{}

%% CTeX
% CJK support, used to show CJK characters in the resume
%
% - fontset=none: disable builtin fontset but instead set the CJK font manually
% - heading=false: disable ctex heading
% - punct=kaiming: use kaiming punctuations styles for CJK
% - scheme=plain: use plain scheme, do not override \normalsize font size
% - space=auto: space settings for CJK characters
%
% ref:
% - http://ctan.mirrorcatalogs.com/language/chinese/ctex/ctex.pdf
\usepackage[UTF8, heading=false, punct=kaiming, scheme=plain, space=auto]{ctex}

\IfFontExistsTF{Noto Serif CJK SC}{
  \setCJKmainfont{Noto Serif CJK SC}
}{}
\IfFontExistsTF{Noto Sans CJK SC}{
  \setCJKsansfont{Noto Sans CJK SC}
}{}

%% line spacing
\usepackage{setspace}
\setstretch{1.125}

%% URL styling - use normal text instead of monospace
\urlstyle{same}

%% Patch \httplink and \httpslink to handle full URLs
% The original moderncv macros always prepend http:// or https:// to URLs.
% This causes issues when the URL already has a protocol (e.g., https://example.com)
% resulting in malformed URLs like https://https://example.com.
% This patch checks if the URL already contains "://" and uses it directly if so.
% Note: We use \str_set:Nx (x-expansion) to expand macros like \@homepage first.
\ExplSyntaxOn
\str_new:N \g_yamlresume_url_str

\RenewDocumentCommand{\httpslink}{O{}m}{
  \str_set:Nx \g_yamlresume_url_str {#2}
  \str_if_in:NnTF \g_yamlresume_url_str {://}
    { \url{#2} }
    { \url{https://#2} }
}

\RenewDocumentCommand{\httplink}{O{}m}{
  \str_set:Nx \g_yamlresume_url_str {#2}
  \str_if_in:NnTF \g_yamlresume_url_str {://}
    { \url{#2} }
    { \url{http://#2} }
}
\ExplSyntaxOff

\name{Vasiliy Polyakov}{}
\title{Senior Software Engineer}
\email{job@vpolyakov.cv}
\homepage{https://vpolyakov.cv/}

\extrainfo{{\small \faLinkedin}\ \href{https://www.linkedin.com/in/invasy/}{@invasy} {} {} {} • {} {} {} 
{\small \faGithub}\ \href{https://github.com/invasy}{@invasy}}

\begin{document}

\maketitle

\section{Basics}

\cvline{}{\begin{itemize}
\item Software engineer (C++/Qt, Scala, Python) with over 10 years of experience in enterprise services development.
\item Development automation specialist with a vast CI/CD and DevOps expertise.
\item Collaborating with distributed teams in different software development stages.
\item Constantly improving skills with new technologies and instruments.
\item Passionate about efficiency and performance.
\item GNU/Linux and FOSS enthusiast.
\end{itemize}}

\section{Work}

\cventry{Jun 2023–Present}
        {Senior Software Engineer}
        {NGENIX}
        {\url{https://ngenix.net/}}
        {}
        {\textbf{Keywords}: Python, Flask, FastAPI, OpenAPI, Connexion, SQLAlchemy, PostgreSQL, ClickHouse, Kubernetes}

\cventry{Dec 2021–Sep 2022}
        {Lead Software Engineer}
        {M.Video-Eldorardo}
        {\url{https://www.mvideoeldorado.ru/}}
        {}
        {\begin{itemize}
\item Analyzed requirements and implemented architecture for new microservices.
\item Collaborated with agile team, managed to enhance service robustness.
\item Facilitated internal developers meetings to share ideas and knowledge.
\end{itemize}
\textbf{Keywords}: Scala, Akka, Lagom, Cassandra, Elastic Stack, SAP, GitLabCI, Kubernetes, microservices}

\cventry{Jan 2019–Dec 2021}
        {Senior Software Engineer}
        {Rostelecom IT}
        {\url{https://www.rt.ru/}}
        {}
        {\begin{itemize}
\item Developed high performance event-driven payment service with C++, Qt, CEF, OpenShift.
\item Boosted service performance by redesigning event queues.
\item Organized and implemented CI/CD pipelines to decrease deployment time from days to minutes.
\item Initiated migration to blue-green deployment with extensive load testing.
\item Planned tasks and facilitated meetings with distributed agile team.
\item Redesigned documentation and knowledge base structure, saved hours of searching for answers.
\end{itemize}
\textbf{Keywords}: C++, Qt, CEF, Scala, Oracle, GitLabCI, Tomcat, OpenShift, JMeter, Gatling}

\cventry{May 2018–Dec 2018}
        {Research Engineer}
        {Perm State University}
        {\url{https://www.psu.ru/}}
        {}
        {\begin{itemize}
\item Participated in research and development project for \textit{UEC-Aviadvigatel} funded by Russian Foundation for Basic Research.
\item Project result is a turbine engine computational aerodynamics model based on a proprietary numerical solver of Navier-Stokes equations.
\end{itemize}
\textbf{Keywords}: C++, Fortran 90, CUDA, OpenMP, OpenMPI, OpenHPC, RHEL, Ganglia}

\cventry{Dec 2017–May 2018}
        {Software Engineer}
        {Stream (MTS)}
        {\url{https://mts.ru/}}
        {}
        {\begin{itemize}
\item Developed in-house high performance service using C++, STL, Boost, Qt that allowed clients to commit payment transactions and view fiscal data.
\item Optimized event matching algorithms to decrease server load by 21\% on average.
\end{itemize}
\textbf{Keywords}: C++, STL, Boost, CMake}

\cventry{Oct 2012–Dec 2017}
        {Chief of Laboratory and Research Engineer}
        {Perm State University}
        {\url{https://www.psu.ru/}}
        {}
        {\begin{itemize}
\item Researched and developed HPC applications (fluid mechanics, aerodynamics, linguistics).
\item Tasks, projects, and people management.
\item HPC clusters administration and maintenance.
\item Popularization of science, public lectures, science events and festivals.
\end{itemize}
\textbf{Keywords}: C++, Fortran90, OpenMP, OpenMPI, CUDA, Hadoop, Perl, Ruby on Rails, Redmine, RHEL, CentOS}

\section{Education}

\cventry{Sep 2007–Aug 2013}
        {Bachelor, Applied mathematics and informatics}
        {Perm State University}
        {\url{https://www.psu.ru/}}
        {}
        {}

\section{Skills}

\cvline{C++}{Expert \hfill \textbf{Keywords}: STL, Boost, Qt, CEF}
\cvline{Scala}{Expert \hfill \textbf{Keywords}: Akka, Cats, Lagom}
\cvline{Python}{Expert \hfill \textbf{Keywords}: Django, Flask, Connexion, asyncio, SQLAlchemy, Pydantic}
\cvline{DB}{Expert \hfill \textbf{Keywords}: PostgreSQL, MySQL, ClickHouse, Cassandra}
\cvline{DevOps}{Expert \hfill \textbf{Keywords}: GitHub Actions, GitLab CI, Jenkins, Ansible, Puppet, Docker, Podman, Kubernetes, GNU Make, Bash}
\cvline{Misc}{Expert \hfill \textbf{Keywords}: Linux, Git, Jira, Confluence, Scrum, Kanban}

\section{Languages}

\cvline{Russian}{Native or Bilingual Proficiency}
\cvline{English}{Full Professional Proficiency}
\end{document}